The expected shape of the Milky Way's Dark Matter halo

### 2018-09-18 Paper/paper.tex
edit

A robust prediction of the Cold Dark Matter (CDM) model is that DM
halos are ellipsoidal and can be characterized by the principal axes
$a>b>c$.  
The ellipsoidal shape is mostly due to the anisotropical and
clumpy accretion of matter influenced by environmental structures.

The general concensus in numerical simulations is that halos tend to
be prolate with axial ratios b/a ~ \textit{number}, $c/a$
~ \textit{number} and small differences may arise by the use different
methods in numerical recipies for the simulations and the
shape-calculation methods  \citep{Allgood_et_al._2006}. Some
studies have gone a step further as for analyzing the dependence of
shape of the DM halo on the radius and redshift
\citep[e.g.][]{Allgood_et_al._2006}, generally
finding that halos are rounder at the outerskirts and at lower
redshift.

\citep{Vera-Ciro_et_al._2011}

@@

Due to the evasive nature of DM, properly constraining the shape of DM halos is a very difficult endeavour.\\

>>>>

A robust prediction of the Cold Dark Matter (CDM) model is that DM
halos are ellipsoidal and can be characterized by the principal axes
$a>b>c$.
The ellipsoidal shape is mostly due to the anisotropical and
clumpy accretion of matter influenced by environmental structures. 
The shape has a strong mass dependence \citep{Allgood_et_al._2006}. 
The general consensus from numerical studies is that Milky Way type
halos tend to be prolate with axial ratios $b/a\approx X$ and  $c/a\approx X$, 
Halos are also found to be rounder at the outerskirts and at lower
redshifts.

@@
